Our Rodent Species

### 2018-02-14 profiles.Rmd
add color pictures

>>>>

  Rodents = c("![](rodent_pictures/color_pictures/BA.png)",
              "![](rodent_pictures/color_pictures/PB.png)",
              "![](rodent_pictures/color_pictures/PH.png)",
              "![](rodent_pictures/color_pictures/PI.png)",
              "![](rodent_pictures/color_pictures/PP.png)",
              "![](rodent_pictures/color_pictures/DM.png)",
              "![](rodent_pictures/color_pictures/DO.png)",
              "![](rodent_pictures/color_pictures/DS.png)",
              "![](rodent_pictures/color_pictures/NA.png)",
              "![](rodent_pictures/color_pictures/OL.png)",
              "![](rodent_pictures/color_pictures/OT.png)",
              "![](rodent_pictures/color_pictures/PF.png)",
              "![](rodent_pictures/color_pictures/PE.png)",
              "![](rodent_pictures/color_pictures/PL.png)",
              "![](rodent_pictures/color_pictures/PM.png)",
              "![](rodent_pictures/color_pictures/RF.png)",
              "![](rodent_pictures/color_pictures/RM.png)",
              "![](rodent_pictures/color_pictures/RO.png)",
              "![](rodent_pictures/color_pictures/SF.png)",
              "![](rodent_pictures/color_pictures/SH.png)",
              "![](rodent_pictures/color_pictures/SO.png)"), 
